---
title: "Flock camera locations"
format: html
name: Sofia Rodas
date: September 2026
message: false
warning: false
---

## Background
Flock cameras are a brand of Automate License Plate Readers (ALPRs) that are being installed throughout the US. ALPRs have been promoted as a tool to combat crime, however in reality they pose privacy risks as they track peoples movements sharing it nationally with participating agencies. ALPRs give users unfounded access to constant data of peoples whereabouts.  Misuse of ALPR data is reported with some of the most malicious uses being police stalking ex-partners.

A movement to remove ALPRs called [DeFlock](https://deflock.org/) is mapping ALPR locations nationwide. This repository explores where ALPRs are located.

## Data Access

The data is publicly collected through crowd sourcing. A publicly accessible [GitHub repository](https://github.com/FoggedLens/deflock-data) explains how to download the data. 

```{r}
# load appropriate libraries
library(tidyverse)
library(sf)
library(tmap)
```

Only run this once as it downloads the data. Unless you're trying to download updated data you don't need to redownload it.
```{r}
#| eval: false

url  <- "https://data.dontgetflocked.com/cameras.geojson.gz"
flock_data <- "cameras.geojson.gz"
download.file(url, flock_data, mode = "wb")
```


```{r}
# read in the data from the downloaded file
cams <- st_read(flock_data)

# view size of the data
print(nrow(cams))

# view the top of the data frame
head(cams)

```

Yay! We downloaded the data!

## Initial investigation
```{r}
tm_shape(cams)+
  tm_dots()
```
Based on this map the ALPRs are located across the US. 

Let's investigate a subsect. 

## ALPR cameras in Los Angeles

As a Los Angeles native I'm most interested in the ALPR distribution in Los Angeles. I downlaoded 
```{r}
# read in Los Angeles neighnorhood shape file
la_neighborhood <- sf::st_read(here::here("..", "fall", "eds-223-geospatial", "eds223-hw1","data","LA_Times_Neighborhood_Boundaries-shp", 
                                          "8494cd42-db48-4af1-a215-a2c8f61e96a22020328-1-621do0.x5yiu.shp"))
```

Make sure the CRS are the same for all of our geospatial items.
```{r}
# ensure the crs match
if_else((st_crs(la_neighborhood) == st_crs(cams)) == "TRUE", 
        "The CRS match!", 
        "The CRS do not match.")
```

Transform the CRS so that they match.
```{r}
la_neighborhood <- st_transform(la_neighborhood, crs = st_crs(cams))
```

Double check that the transformation was successful.
```{r}
# ensure the crs match
if_else((st_crs(la_neighborhood) == st_crs(cams)) == "TRUE", 
        "The CRS match!", 
        "The CRS do not match.")
```

Map only LA County ALPRs.
```{r}
tm_shape(cams)+
    tm_dots(fill_alpha = 0.5)+ 
  tm_shape(la_neighborhood, is.main = TRUE)+
    tm_borders()
```

This map shows the ALPRs that are within the bounding box of LA County but this looks messy since some of the points aren't within the polygons. Let's create a new data set for only those points that are within the polygons. 


```{r}

```



## References
- LA Times. (2016). LA Times Neighborhood Boundaries. Retrieved from [URL](https://geohub.lacity.org/datasets/d6c55385a0e749519f238b77135eafac_0/about)


